Psychological Needs During Intergroup Contact

### 2022-01-04 Methods-and-Results.Rmd
descr tables added

>>>>

```{r CombinedDescriptivesTbl, include=FALSE}

# ALTERNATIVE:
# Full Sample Descriptives Table [longer format (Descriptives below correlations)]
rbind(
  workerMlCor %>%
    rownames_to_column(., "Variable") %>%
    mutate(Allport = ""),
  studentMlCor %>%
    select(names(workerMlCor)) %>%
    rownames_to_column(., "Variable") %>%
    mutate(Allport = ""),
  medicalMlCor %>%
    select(names(workerMlCor), "Allport") %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  pack_rows("Study 1", 1, nrow(workerMlCor)) %>%
  pack_rows("Study 2", nrow(workerMlCor) + 1,
            sum(nrow(workerMlCor), nrow(studentMlCor))) %>%
  pack_rows("Study 3", sum(nrow(workerMlCor), nrow(studentMlCor)) + 1,  
            sum(nrow(workerMlCor), nrow(studentMlCor), nrow(medicalMlCor))) %>%
  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrFullLong.tex")

# Full Sample Descriptives Table [wider format (descriptives next to correlation)]
rbind(
  workerMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  studentMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  medicalMlCor %>%
    select(names(workerMlCor), "Allport") %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1)))  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(medicalMlCor),
      "Descriptives" = nrow(medicalMlCor) - ncol(medicalMlCor)
    )
  ) %>%
  pack_rows("Study 1", 1, ncol(workerMlCor)) %>%
  pack_rows("Study 2", ncol(workerMlCor) + 1,
            sum(ncol(workerMlCor), ncol(studentMlCor))) %>%
  pack_rows("Study 3", sum(ncol(workerMlCor), ncol(studentMlCor)) + 1,  
            sum(ncol(workerMlCor), ncol(studentMlCor), ncol(medicalMlCor))) %>% # fix table position
  save_kable("Tables/descrFullWide.tex")

# Outgroup Interaction Sample Descriptives Table
rbind(
  workerOutMlCor %>%
    rownames_to_column(., "Variable") %>%
    mutate(Allport = ""),
  studentOutMlCor %>%
    select(names(workerOutMlCor)) %>%
    rownames_to_column(., "Variable") %>%
    mutate(Allport = ""),
  medicalOutMlCor %>%
    select(names(workerOutMlCor), "Allport") %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  pack_rows("Study 1", 1, nrow(workerOutMlCor)) %>%
  pack_rows("Study 2", nrow(workerOutMlCor) + 1,
            sum(nrow(workerOutMlCor), nrow(studentOutMlCor))) %>%
  pack_rows("Study 3", sum(nrow(workerOutMlCor), nrow(studentOutMlCor)) + 1,  
            sum(nrow(workerOutMlCor), nrow(studentOutMlCor), nrow(medicalOutMlCor))) %>%
  gsub("\\hspace{1em}Grand Mean", "\\addlinespace\n\\hspace{1em}Grand Mean", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrOutLong.tex")

# Outgroup Interaction Sample Descriptives Table --- wider version
rbind(
  workerOutMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  studentOutMlCor %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable") %>%
    add_column(Allport = "",
               .before = "Grand Mean"),
  medicalOutMlCor %>%
    select(names(workerOutMlCor), "Allport") %>%
    t %>%
    as.data.frame %>%
    rownames_to_column(., "Variable")
) %>%
  kbl(.,
      format = "latex",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  pack_rows("Study 1", 1, ncol(workerOutMlCor)) %>%
  pack_rows("Study 2", ncol(workerOutMlCor) + 1,
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor))) %>%
  pack_rows("Study 3", sum(ncol(workerOutMlCor), ncol(studentOutMlCor)) + 1,  
            sum(ncol(workerOutMlCor), ncol(studentOutMlCor), ncol(medicalOutMlCor))) %>% 
  save_kable("Tables/descrOutWide.tex")

\input{Tables/descrFullWide}
\input{Tables/descrOutWide}
